---
title: "BlankmanF Function Documentation"
author: "Holden Blank"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(BlankmanF)
```

## Overview

The `BlankmanF` package provides tools for conducting and visualizing the Friedman test. This vignette introduces the main functions of the package with usage examples.

---

## Function: `run_friedman_test()`

This function performs the Friedman test and returns a custom S3 object of class `blankman_result`.

```{r}
example_data <- data.frame(
  Subject = rep(1:6, each = 3),
  Treatment = rep(c("A", "B", "C"), times = 6),
  Score = c(85, 88, 90, 78, 80, 82, 91, 93, 92, 87, 89, 90, 70, 72, 74, 76, 77, 79)
)

result <- run_friedman_test(example_data, "Subject", "Treatment", "Score")
```

By default, printing the result uses the S3 method:

```{r}
result  # uses print.blankman_result()
```

---

## Function: `plot_friedman_ranks()`

This function visualizes mean ranks of treatments using a bar plot.

```{r}
plot_friedman_ranks(example_data, "Subject", "Treatment", "Score")
```

---

## Function: `get_friedman_summary()`

This function returns a tidy summary of mean and standard deviation of ranks by treatment.

```{r}
get_friedman_summary(example_data, "Subject", "Treatment", "Score")
```

---

## Notes

- The package expects tidy, long-format data.
- `run_friedman_test()` returns an S3 object with a custom print method for cleaner output.
- Designed for flexibility and extension (e.g., post-hoc tests in future versions).
